r5r: Rapid Realistic Routing with R5 in R

### 2020-09-15 r-package/paper2020/paper2020.Rmd
paper paragraph 2 done

...

@@

The **r5r** package provides a simple and convenient friendly interface to R<sup>5</sup>, [Rapid Realistic Routing on Real-world and Reimagined networks](https://github.com/conveyal/r5). The  developed by [Conveyal](https://www.conveyal.com/).

papers under R5 we should cite
- https://repository.asu.edu/items/54162
- https://www.jtlu.org/index.php/jtlu/article/view/1074

>>>>

This paper presents [r5r](https://ipeagit.github.io/r5r/), a new open source 
R package for rapid realistic routing on multimodal transport networks based on
the [Rapid Realistic Routing on Real-world and Reimagined networks (R<sup>5</sup>)](https://github.com/conveyal/r5). R<sup>5</sup> is a powerful 
next-generation routing engine written in Java and developed at Conveyal (ref 1-2)
to replace its predecessor OpenTripPlanner. The r5r package provides a simple 
and friendly interface to run R<sup>5</sup> locally from within R, what allows 
users to efficiently calculate travel time matrices or generate multiple route 
alternatives between origins and destinations using seamless parallel computing.
1 - https://repository.asu.edu/items/54162
2- https://www.jtlu.org/index.php/jtlu/article/view/1074

@@

p
